Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-10-04 files/Overview.tex
Overview v1

\subsubsection{Chapter 1}
This dissertation is a literature study that investigates the validity of different linear models. The term validity in this dissertation means how well a model compares to a more realistic model for real world applications. The first chapter of the dissertation introduces the models. The main model is the Timoshenko beam theory.

\subsubsection{Chapter 2}
\subsubsection{Chapter 3}
\subsubsection{Chapter 4}
\subsubsection{Chapter 5}
\subsubsection{Chapter 6}

>>>>

\subsubsection{Chapter 1}
This dissertation is a literature study that investigates the validity of different linear models. The term validity in this dissertation means how well a model compares to a more realistic model for real world applications. The first chapter of the dissertation introduces the models. The main model is the Timoshenko beam theory. The other models are a two-dimensional elastic model, a three-dimensional elastic model and a Reissner-Mindlin plate model. The goal of this disseration to validate the use of the Timoshenko beam model and the Reissner-Mindlin plate model in applications. These models are simplified one-dimensional beam and two-dimensional plate models. But more realistic models exists, such as a two-dimensional and three-dimensional beam model and a three-dimensional plate model. Using modal analysis, it is shown that the solutions of the models can be represented as a linear combination of the eigenvalues and eigenfunctions. Therefore it is only required to compare the eigenvalues and eigenfunctions of the models to determine the difference of the solutions.

\subsubsection{Chapter 2}
In this section, the existence and solutions for a general vibration problem is investigated. The main article that is discussed is \cite{VV02}. In this article, the authors define a general vibration problem. The authors state four assumptions that need to be satified. Under these four assumptions, it can be shown that for the general vibration problem there exists a linear operator A, which is an infinitesimal generator of a $C_0$-semigroup of contractions with a domain in the problem space. This operator allows the general vibration problem to be rewritten as a system of first order differential equations $\displaystyle x' = Ax + f$. This differential equations are rewritten into an initial value problem which can be proven using semi-group theory to have a unique solution. The authors then provide the necessary proofs to show that a solution of the initial value problem is also a solution of the general vibration problem. An example of the application of this theory is provided using a cantilever Timoshenko beam.

\subsubsection{Chapter 3}
\subsubsection{Chapter 4}
\subsubsection{Chapter 5}
\subsubsection{Chapter 6}
